An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
Fix braces
add temporal path figure

We can analyze the spread of information between $A$, $B$, and $C$
as a process on a graph that changes over time.
Such graphs are known as evolving graphs.
% Evolving graphs are models to study this kind of scenario where the
% interrelations between entities are time-dependent.
% We assume that the reader is familiar with the basic graph terminology.
% All the necessary material can be found in}.
We follow the notation of (static) graphs in \cite{even12,kegi11}.
In general, a evolving graph $G(t) = (V(t), E(t))$ is  a graph where the node set
and edge set are functions of time $t$.
However, in different literature the term ``evolving graph'' has been
used to refer to slightly different models.
 Flajolet et al. \cite{fkp89} use the term to mean the evolution of random graphs.
Bahmani et al. \cite{bkmu12} use the term to mean a sequence of graphs where
the difference between two consecutive graphs is small.
Similar models are also investigated using the term ``evolving network'' and
``time-dependent graph''.

@@

\subsection{Algebraic Evolving-Graph BFS}
\label{sec:representation}
As before, let $G_n = \langle G^{[1]}, G^{[2]}, \ldots, G^{[n]}\rangle$ be an evolving graph with $n$ time stamps. For each graph $G^{[t]}$, we use $A^{[t]}$ to denote
the corresponding adjacency matrix.
\[
A^{[t]}(i,j) =
\begin{cases}
 1 & \mbox{if $(i,j)$ is an edge of $G^{[t]}$,} \\
 0 & \mbox{otherwise.}
\end{cases}
\]
 Each $A^{[t]}$ can be represented by
a $|V|\times |V|$ sparse matrix,
where $|V|$ is the total number of nodes in $G_n$.
We use a sequence of adjacency matrices $A_n = \langle A^{[1]}, A^{[2]}, \ldots, A^{n]}\rangle$ to represent $G_n$.
For example, the evolving graph in Figure \ref{fig:eg_shortest_path}
can be represented as
\[
\Big\langle
  \begin{bmatrix}
    0 & 1 & 0 \\
    0 & 0 & 0 \\
    0 & 0 & 0
  \end{bmatrix},~
 \begin{bmatrix}
   0 & 0 & 1 \\
   0 & 0 & 0 \\
   0 & 0 & 0
 \end{bmatrix},~
 \begin{bmatrix}
  0 & 0 & 0 \\
  0 & 0 & 1 \\
  0 & 0 & 0
 \end{bmatrix}
\Big\rangle
\]

@@

\subsection{Aggregated Graphs}
\label{sec:aggregated-graphs}

In this section, we answer the question why we need evolving graph.

At the beginning of the paper, we set up a game played by three people $A$, $B$,
and $C$ and we showed if

@@

>>>>

We can analyze the spread of information between $A$, $B$, and $C$
as a process on a graph that changes over time.
Such graphs are known as evolving graphs.
% Evolving graphs are models to study this kind of scenario where the
% interrelations between entities are time-dependent.
% We assume that the reader is familiar with the basic graph terminology.
% All the necessary material can be found in}.
We follow the notation of (static) graphs in \cite{even12,kegi11}.
In general, an evolving graph $G(t) = (V(t), E(t))$ is  a graph where the node set
and edge set are functions of time $t$.
However, in different literature the term ``evolving graph'' has been
used to refer to slightly different models.
 Flajolet et al. \cite{fkp89} use the term to mean the evolution of random graphs.
Bahmani et al. \cite{bkmu12} use the term to mean a sequence of graphs where
the difference between two consecutive graphs is small.
Similar models are also investigated using the term ``evolving network'' and
``time-dependent graph''.

@@

\subsection{Algebraic Evolving-Graph BFS}
\label{sec:representation}
As before, let $G_n = \langle G^{[1]}, G^{[2]}, \ldots, G^{[n]}\rangle$ be an evolving graph with $n$ time stamps. For each graph $G^{[t]}$, we use $A^{[t]}$ to denote
the corresponding adjacency matrix.
\[
A^{[t]}(i,j) =
\begin{cases}
 1 & \mbox{if $(i,j)$ is an edge of $G^{[t]}$,} \\
 0 & \mbox{otherwise.}
\end{cases}
\]
 Each $A^{[t]}$ can be represented by
a $|V|\times |V|$ sparse matrix,
where $|V|$ is the total number of nodes in $G_n$.
We use a sequence of adjacency matrices $A_n = \langle A^{[1]}, A^{[2]}, \ldots, A^{n]}\rangle$ to represent $G_n$.
For example, the evolving graph in Figure \ref{fig:eg_shortest_path}
can be represented as
\[
\left\langle
  \begin{bmatrix}
    0 & 1 & 0 \\
    0 & 0 & 0 \\
    0 & 0 & 0
  \end{bmatrix},~
 \begin{bmatrix}
   0 & 0 & 1 \\
   0 & 0 & 0 \\
   0 & 0 & 0
 \end{bmatrix},~
 \begin{bmatrix}
  0 & 0 & 0 \\
  0 & 0 & 1 \\
  0 & 0 & 0
 \end{bmatrix}
\right\rangle
\]

@@

% \subsection{Aggregated Graphs}
% \label{sec:aggregated-graphs}

% % In this section, we answer the question why we need evolving graph.
% % 
% At the beginning of the paper, we set up a game played by three people $A$, $B$,
% and $C$ and we showed if $A$ and $B$

@@

\begin{figure}[h]
 \begin{center}
    \begin{tikzpicture}[scale=.36, line width =1.4pt]
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};

  \foreach \from/\to in {n10/n7, n11/n12}
   \draw[every edge,->] (\from) -- (\to);
     \draw[dotted,->](n1) -- (n4);
  \draw[dotted,->](n10) -- (n1);
  \draw[dotted,->](n4) -- (n12);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
   \begin{tikzpicture}[scale=.36, line width =1.4pt]
  \node[circle,fill=green1, minimum size=0.2cm] (n7) at (-5,7) {2};
  \node[circle,draw=red1, minimum size=0.2cm] (n8) at (-10,5) {3};
  \node[circle,fill=green1, minimum size=0.2cm] (n10) at (-8,10) {1};

  \foreach \from/\to in {n1/n4}
   \draw[every edge,->] (\from) -- (\to);
     \draw[dotted,->](n7) to[out=70, in=40] (n11);
  \draw[dotted,->](n10) -- (n7);
   \draw[dotted,->](n11) -- (n12);
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(4,3) -- (-2,3) node [midway,yshift=-0.6cm]{ $t_2$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(-4,3) -- (-10.5,3) node [midway,yshift=-0.6cm]{ $t_1$};
\draw [decorate,decoration={brace,amplitude=5pt},xshift=-4pt,yshift=0pt]
(11.5,3) -- (5.5,3) node [midway,yshift=-0.6cm]{ $t_3$};
    \end{tikzpicture}
\end{center}
\caption{An evolving graph with 3 time stamps $t_1$, $t_2$ and $t_3$.
The back dashed lines indicate a temporal path from $(1, t_1)$ to $(3,t_3)$.}
\label{fig:active}
\end{figure}
